Fast approximate Bayesian inference of HIV indicators using PCA adaptive Gauss-Hermite quadrature

### 2025-08-12 src/docs_paper-jtb/paper.Rmd
Clearer exposition about compute time

Inference with NUTS took `r naomi_time_tmbstan_hours` hours (across 18 cores), while inference with GPCA-AGHQ took `r naomi_time_aghq_hours` hours and GEB just `r naomi_time_tmb_hours` hours (equivalent to `r naomi_time_tmb_minutes` minutes) both on a laptop.
The NUTS and GPCA-AGHQ algorithms can be run under a range of settings, trading off accuracy and run-time.

>>>>

Inference with NUTS took `r naomi_time_tmbstan_hours` hours (across 18 cores, i.e. over 50 days of compute time) running on a high performance computing cluster.
Meanwhile, inference with GPCA-AGHQ took `r naomi_time_aghq_hours` hours and GEB just `r naomi_time_tmb_hours` hours (equivalent to `r naomi_time_tmb_minutes` minutes), both running on a laptop.
The NUTS and GPCA-AGHQ algorithms can be run under a range of settings, trading off accuracy and run-time.
